
---
title: Kyaukmasin Resreve_Biomass collected to modify MyanmarSelection System for
  forest management
output:
  html_document:
    df_print: paged
---

In myanmar, 1.4 % of the total forest is being lost annually.Myanmar Selection System known as Burma Selection System developed by British in 1880s is still being applied for the sustainable forest management in Myanmar. Forest Department of Myanmar is planning to modify the system in order to accomodate with present forest situation. FD, therefore, conducted a forest inventory at the compartment number 20 of the Kyaukmasin Reserve located in Bago Mountain range also known as home of teak in Myanmar. The specific object of the inventory are 
to explore the species compositon of the Reserve forest;
to study the natural regeneration fo the reserve forest;
to formulate the appropriate silvicultural approaches; and 
to support Myanmar Selection System for logging.

All the trees which are above 5 cm are measured in an area of 180.16 ha.  

```{r}

rm(list = ls())

# install.packages("tidyverse")
# install.packages("lubridate")
# install.packages("BIOMASS")

library(tidyverse)
library(lubridate)
library(BIOMASS)

```
```{r}
setwd("D:/Google Drive (Uni)/PhD_Cambridge/First Year Report/R_First_Year_Calculation/Data")
Kyaukmasin_MSS <- read.csv("KMS_MSS.csv")
head(Kyaukmasin_MSS)
str(Kyaukmasin_MSS)
class(Kyaukmasin_MSS)

```

```{r}
Taxo <- correctTaxo(genus=Kyaukmasin_MSS$Genus,species = Kyaukmasin_MSS$Species)

Kyaukmasin_MSS$genusCorr <- Taxo$genusCorrected
Kyaukmasin_MSS$speciesCorr <- Taxo$speciesCorrected

APG <- getTaxonomy(Kyaukmasin_MSS$genusCorr, findOrder =T)
Kyaukmasin_MSS$familyAPG <- APG$family
Kyaukmasin_MSS$orderAPG <- APG$order

dataWD <- getWoodDensity(genus=Kyaukmasin_MSS$genusCorr,
                       species=Kyaukmasin_MSS$speciesCorr,
                       stand=Kyaukmasin_MSS$plotId)

sum(dataWD$levelWD == "species")

sum(dataWD$levelWD == "genus")

sum(!dataWD$levelWD%in%c("genus","species"))
# 
# WrongNames <- filter(Taxo, nameModified == TRUE)

```

Height Estimation and Biomass Biomass Calculation
The geo-positions of Kyaukmasin Reserve (UTM) is used to formulate Height Model as I do not have  Height data. 

```{r}
Kyaukmasin_MSS$WD=dataWD$meanWD

myll<-cbind(rep(95.853417, nrow(Kyaukmasin_MSS)),rep(19.43822,nrow(Kyaukmasin_MSS)))

AGBtree<-computeAGB(D=Kyaukmasin_MSS$Dbh_cm,
                    WD=Kyaukmasin_MSS$WD, coord = myll)




AGB_total_Kyaukmasin_MSS <- Kyaukmasin_MSS %>%  mutate(AGB_Total = AGBtree)

KMSS <- AGB_total_Kyaukmasin_MSS

```

#Converting to Ha scale biomass

```{r}
ABG_ha <- sum(AGB_total_Kyaukmasin_MSS$AGB_Total)/180.16

```











